\section{Bounds: contradiction radius}\label{sec:contradiction}

Theorem~\ref{thm:bounds} returns an interval; a public claim returns a point. The diagnostic measures their distance after standardising each input by its measurement uncertainty.

\begin{definition}[Feasible set]\label{def:feasible}
For inputs $x=(\omega,w,a,f,M,D)$ and exposure range $[\mu_{\mathrm{lo}},\mu_{\mathrm{hi}}]$,
\begin{equation}\label{eq:feasible}
\mathcal F(x)=
\Bigl\{q\in[0,1]:\;
\exists\,\mu\in[\mu_{\mathrm{lo}},\mu_{\mathrm{hi}}]\;\text{with}\;
q=1-\omega\tfrac{w+\mu(a-f)}{w}
\;\text{and}\; qD\le M\Bigr\}.
\end{equation}
\end{definition}

A claim $\hat D_M^{(i)}$ converts to $q^{(i)}=\hat D_M^{(i)}/\hat D$ and is feasible iff $q^{(i)}\in\mathcal F(\hat x)$.

\begin{definition}[Contradiction radius]\label{def:radius}
Let $\hat x=(\hat\omega,\hat w,\hat a,\hat f,\hat M,\hat D)$ with measured standard errors $\sigma_\omega,\sigma_w,\sigma_M$. The contradiction radius of claim $q^{(i)}$ is
\begin{equation}\label{eq:rho}
\rho^{(i)}
=\inf_{\omega',w',M'}\;
\max\!\left\{
\tfrac{|\omega'-\hat\omega|}{\sigma_\omega},\;
\tfrac{|w'-\hat w|}{\sigma_w},\;
\tfrac{(M'-\hat M)_+}{\sigma_M}
\right\}
\quad\text{s.t.}\quad
q^{(i)}\in \mathcal F((\omega',w',\hat a,\hat f,M',\hat D)).
\end{equation}
\end{definition}

\begin{theorem}[Feasibility and contradiction]\label{thm:contradiction}
With $(\hat a,\hat f,\hat D)$ and the exposure range fixed, a claim is consistent with the independent inputs iff $\rho^{(i)}=0$. If $\rho^{(i)}>0$, every rationalisation $(\omega',w',M')$ makes at least one \emph{penalised} displacement---$|\omega'-\hat\omega|/\sigma_\omega$, $|w'-\hat w|/\sigma_w$, or $(M'-\hat M)_+/\sigma_M$---of at least $\rho^{(i)}$ standard-error units. (Lowering $M$ is unpenalised because it can only shrink the feasible set.)
\end{theorem}

\paragraph{Interpretation.} The contradiction radius answers the question a motivated critic must eventually face: \emph{which measurement, exactly, do you say is wrong, and by how much?} A claim with $\rho=0$ is compatible with all independent inputs; nothing more can be said against it on this evidence. A claim with $\rho=2$ requires some input to be off by two standard errors---uncomfortable but conceivable. A claim with $\rho=20$ requires an independently measured quantity to be wrong by twenty standard errors, an error that measurement noise cannot produce; defending such a claim requires asserting institutional fabrication, and the radius names the institutions and the magnitudes. Because $\rho$ standardises by \emph{measured} uncertainty, it is unit-free and comparable across conflicts and across claims. It is also symmetric: an implausibly \emph{low} combatant claim generates a positive radius the same way an implausibly high one does. What the radius is not: it is not a posterior probability, it does not weigh how \emph{many} inputs must move (only the largest single standardised move), and it inherits any systematic---as opposed to sampling---error in the inputs, which is why Section~\ref{sec:gaza} reports it under every anchor choice.

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  >=Stealth, font=\small,
  vert/.style={circle,draw=black!75,fill=white,inner sep=1.5pt,minimum size=4mm},
  feas/.style={fill=blue!10,draw=blue!55,thick},
  arr/.style={->,>=Stealth,gray!70,thick},
  lab/.style={font=\footnotesize,inner sep=2pt}
]
\coordinate (T)  at ( 0   , 2.5);
\coordinate (BL) at (-3.0 ,-0.9);
\coordinate (BR) at ( 3.0 ,-0.9);

\draw[feas] (T) -- (BL) -- (BR) -- cycle;
\node[lab,align=center] at (0,0.55) {feasible set\\$\mathcal F(\hat x)$};

\node[vert,fill=blue!55] (P) at (0.4, 0.0) {};
\node[lab,below=1pt of P] {feasible $\hat q$};

\node[vert,fill=red!70] (Q) at (4.7,0.95) {};
\node[lab,right=1pt of Q] {disputed $q^{(\mathrm{IDF})}$};

\draw[arr] (Q) -- ($(T)!0.18!(Q)$)  node[midway,above,sloped,font=\scriptsize] {$\rho_\omega$};
\draw[arr] (Q) -- ($(BR)!0.20!(Q)$) node[midway,below,sloped,font=\scriptsize] {$\rho_M$};
\draw[arr] (Q) -- ($(BL)!0.30!(Q)$) node[midway,above,sloped,font=\scriptsize] {$\rho_w$};

\node[lab] at (T)  [above=2pt] {$\hat\omega$ axis (demographic deaths)};
\node[lab] at (BL) [below left=1pt,align=center]  {$\hat w$ axis\\(population)};
\node[lab] at (BR) [below right=1pt,align=center] {$\hat M/D$ axis\\(manpower)};
\end{tikzpicture}
\caption{\textbf{Contradiction triangle (conceptual schematic).} The feasible set $\mathcal F$ is bounded by three independently measured ``axes''; the contradiction radius $\rho=\min(\rho_\omega,\rho_w,\rho_M)$ is the shortest standardised perturbation from a disputed claim into $\mathcal F$. Each axis is owned by a different institution, which is what makes the relation under-fudgible: rescuing a claim on one axis leaves fingerprints on that axis's measurement.}
\label{fig:contradiction-triangle}
\end{figure}

\paragraph{Computation.} Because $q(\mu)$ is monotone, the boundary of $\mathcal F$ is attained on one of three axes: the demographic axis ($\omega$ moves), the population-composition axis ($w$), or the manpower axis ($M/D$). This is the contradiction triangle of Figure~\ref{fig:contradiction-triangle}; \eqref{eq:rho} is a low-dimensional convex programme.

\paragraph{Diagnostic procedure.}
\begin{enumerate}[label=\textbf{D\arabic*.},leftmargin=*]
\item Fix the analysis window and total deaths $D$; carry the uncertainty in $D$ as a sensitivity dimension, not a constant.
\item Estimate $(w,a)$ from the population baseline and $\omega$ from identified-deaths records, checking each candidate $\omega$ source for selection mechanisms before use.
\item Calibrate the exposure range $[\mu_{\mathrm{lo}},\mu_{\mathrm{hi}}]$ from historical conflicts with known combatant status, and take an independent upper bound on $M$.
\item Compute $\mathcal F(\hat x)$ from \eqref{eq:feasible}.
\item For every disputed $\hat D_M^{(i)}$, report $q^{(i)}=\hat D_M^{(i)}/D$, the membership $q^{(i)}\in\mathcal F$, and $\rho^{(i)}$, under each anchor and each $D$ scenario.
\end{enumerate}
The test is symmetric: it rejects ``too many combatants'' and ``zero combatants'' against the same set.
