\section{Discussion}\label{sec:discussion}

\paragraph{What the paper claims, and what it does not.} The conceptual contribution is the contradiction triangle (Theorem~\ref{thm:contradiction}): no single number can be manipulated without forcing matching deviations in independently-measured quantities, and the contradiction radius $\rho$ gives a unit-free measure of how far a claim sits from the consensus-feasible set. Whereas \citet{spagat2009} frame war-death estimation as an \emph{arena of contestation}, our framework gives the analyst a numerical referee for that arena, in the spirit of \citet{lumpricebanks2013} for multiple systems estimation and \citet{radford2023} for Bayesian source aggregation. In the Gaza application the referee's ruling is deliberately modest: the data bound the combatant share of direct deaths at $25\%$ with no behavioural assumptions and at about $6\%$ under empirically calibrated exposure, and the public claim of $24$--$36\%$ is rejected under every anchor and every calibrated exposure assumption we examined---its upper endpoint is arithmetically infeasible outright, and its lower endpoint survives only by asserting that civilian men were no more exposed than women and children ($\mu\approx 1$), against the calibration evidence. The paper does \emph{not} claim that the spatial model's $q=2.5\%$ is the truth; that number is one prior-dependent point inside the set, reported with its full model documentation so that readers can locate exactly which assumptions produce it.

\paragraph{Where the power comes from.} It is worth being explicit about why the bound binds. The demographic relation has one free behavioural parameter, the exposure ratio $\mu$, and the data pin the product, not the factors: a given deficit of women and children among the dead can be explained by combatants dying, by civilian men being more exposed, or by a mixture. High-combatant claims must therefore assert that $\mu\approx 1$---that civilian men in an urban war were no more exposed than women and children---at the same time as independent calibrations on conflicts with recorded combatant status put $\mu$ at $2$ or higher \citep{frost2026,cockerill2024}. The claim is not rejected by any single measurement but by the joint configuration; that is the under-fudgibility mechanism doing its work, and it is also why the diagnostic is hard to game: an actor wishing to defeat it must coordinate distortions across a census bureau, a health ministry's death records, foreign military-balance assessments, and historical calibration data that predate the conflict.

\paragraph{Relation to convergent evidence.} The convergence table (Table~\ref{tab:convergence}) is, to our knowledge, the first side-by-side placement of the demographic-decomposition literature, the named-combatant documentary record, and a generative spatial model on the same scale. We read the residual disagreement---roughly $q\in[2\%,25\%]$---as an honest statement of what current public data cannot resolve: it is exactly the width of the exposure-calibration question plus the classification question (who counts as a combatant, on which the named-list evidence and demographic methods can legitimately differ). Narrowing it further requires either a defensible conflict-specific measurement of $\mu$ or transparent, auditable combatant lists, not another aggregation rule.

\paragraph{Limitations.}
\begin{enumerate}[leftmargin=*]
\item Class $\mathrm{AM}$ is treated as a single bucket; finer age partitions (18--29, 30--49, 50$+$) tighten the bounds when age-resolved data exist, and the calibration of $\mu$ from near-cutoff age bands \citep{frost2026} is itself subject to sampling noise in small historical samples.
\item The exposure range $[\mu_{\mathrm{lo}},\mu_{\mathrm{hi}}]$ is imported from historical calibration; if the present conflict's exposure structure is genuinely outside that range, only the exposure-agnostic bound and the manpower bound survive. We report both throughout for this reason.
\item The radius standardises by \emph{sampling} error; systematic error in an anchor (e.g.\ selection in who gets recorded as dead) is addressed by re-computing under alternative anchors, not by the radius itself. Section~\ref{sec:gaza} therefore reports all anchors, with the most claim-favourable one as primary.
\item The radius is conservative for non-Gaussian errors; a bootstrap or non-parametric posterior is preferred for small demographic samples.
\item Combatant status is a legal-institutional category, not a demographic one. The framework bounds the share of deaths attributable to members of armed groups as counted by manpower estimates; disputes about who should count as a combatant move $M$ and the interpretation of named lists, and enter the diagnostic through those channels.
\item The framework does not identify indirect deaths from blockade, famine, or healthcare collapse; these require separate excess-mortality methodology \citep{checchiroberts2008,burnham2006,degommeguhasapir2010,gomez2025} and enter only via the denominator $D$, which we vary as a sensitivity dimension.
\end{enumerate}

\paragraph{Reproducibility.} All bounds, radii, and table entries in this paper are generated by a validation script that recomputes them from the raw inputs and fails on any discrepancy. In addition, the algebraic core of the framework (Appendix~\ref{app:proofs}) is formalised and machine-checked in Lean~4 with mathlib, and the remaining results are verified symbolically and numerically by dedicated scripts. Code, the formal proofs, the spatial simulator, and all inputs are available in the companion repository.
