\appendix

\section{Proofs}\label{app:proofs}

The identities, monotonicity statements, and optimality inequalities appearing in these proofs---together with the application arithmetic of Section~\ref{sec:gaza}, over exact rationals---have additionally been machine-checked in Lean~4 with mathlib; the development compiles with no unproven statements and is in the \texttt{formal/} directory of the companion repository, which documents exactly which statement corresponds to which theorem below. Steps involving posteriors, quantiles, and limits are formalised only in simplified kernel form there; for those, the proofs below are the complete argument, and they are additionally exercised by the symbolic and Monte-Carlo checks in the repository's verification scripts.

\begin{proof}[Proof of Theorem~\ref{thm:bounds}]
Throughout, $w>0$ and $f\le a$, so $w+\mu(a-f)>0$ for every $\mu\ge 0$ and all denominators below are positive; the inputs $(\omega,w,a,f)$ are treated as population quantities (sampling error enters separately through the delta method of Section~\ref{sec:bounds}). Let $\lambda$ be the civilian per-capita death hazard in the women-and-children class $W$, so class $\mathrm{AM}$ civilians have hazard $\mu\lambda$. Expected civilian deaths in $W$ and in civilian-$\mathrm{AM}$ are $\lambda w N$ and $\lambda\mu(a-f)N$, so the share of \emph{civilian} deaths landing in $W$ is $w/(w+\mu(a-f))$. Combatant deaths land in $\mathrm{AM}$, so only the civilian fraction $1-q$ of deaths reaches $W$:
\[
\omega=(1-q)\,\frac{w}{w+\mu(a-f)},
\]
which solves to \eqref{eq:qmu}; moreover $\partial_\mu q=-\omega(a-f)/w\le 0$, so $q(\mu)$ is nonincreasing (strictly decreasing unless $\omega=0$ or $a=f$).

\emph{Attainability.} Fix $\mu^\ast\in[\mu_{\mathrm{lo}},\mu_{\mathrm{hi}}]$ with $q(\mu^\ast)\in(0,1)$ and any $\lambda>0$ small enough that the implied class death counts stay below the class populations. The configuration with combatant share $q(\mu^\ast)$ and hazards $(\lambda,\mu^\ast\lambda)$ reproduces the observed $\omega$ exactly, so $q(\mu^\ast)$ cannot be excluded by the data. Boundary values are attained in the closure: $q(\mu^\ast)=1$ forces $\omega=0$ (no civilian deaths, the limit $\lambda\downarrow 0$), and $q(\mu^\ast)=0$ is attained directly with $\lambda>0$ and no combatant deaths.

\emph{Sharpness.} Conversely, any configuration consistent with the model has some $\mu\in[\mu_{\mathrm{lo}},\mu_{\mathrm{hi}}]$, and the display then forces $q=q(\mu)$. Since $\mu\mapsto q(\mu)$ is continuous and monotone, the set of attainable values is exactly the interval $[q(\mu_{\mathrm{hi}}),q(\mu_{\mathrm{lo}})]$; intersecting with $[0,1]$, the logical range of a share, gives the identified set. The benchmark identity \eqref{eq:ident} is the case $\mu=1$, using $w+a=1$. Corollary~\ref{cor:popbudget} follows since $D_M\le M$ and $D>0$ give $q=D_M/D\le M/D$; the joint set is the intersection of two intervals and is empty exactly when the stated endpoints fail to be ordered.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:agg}]
A linear combination $\sum_i c_i\hat\theta_i$ of independent unbiased sources is unbiased iff $\sum_i c_i=1$, and its variance is $\sum_i c_i^2\sigma_i^2$. By Cauchy--Schwarz,
\[
1=\Bigl(\sum_i c_i\Bigr)^{\!2}
=\Bigl(\sum_i (c_i\sigma_i)\cdot\sigma_i^{-1}\Bigr)^{\!2}
\le\Bigl(\sum_i c_i^2\sigma_i^2\Bigr)\Bigl(\sum_i \sigma_i^{-2}\Bigr),
\]
so $\sum_i c_i^2\sigma_i^2\ge\bigl(\sum_i\sigma_i^{-2}\bigr)^{-1}=\hat\sigma_{\mathrm{agg}}^2$, with equality iff $c_i\sigma_i\propto\sigma_i^{-1}$, i.e.\ $c_i\propto\sigma_i^{-2}$---the weights in \eqref{eq:agg}. The bias expression is linearity of expectation: $\E\sum_i c_i\hat\theta_i-\theta=\sum_i c_i b_i$ with $c_i=\hat\sigma_{\mathrm{agg}}^2/\hat\sigma_i^2$.

For the contamination statement, write $\hat\theta_i=\theta+e_i+Z_i\Delta_i$, where $e_i$ is the honest (mean-zero) error, $Z_i\in\{0,1\}$ indicates contamination ($\E Z_i\le\varepsilon_i$), and $\Delta_i$ is the contaminating displacement, which by hypothesis satisfies $|\Delta_i|\le R_i$ (the contaminating support lies in a set of diameter $R_i$ containing the truth). Then
\[
\bigl|\E\hat\theta_{\mathrm{agg}}-\theta\bigr|
=\Bigl|\sum_i c_i\,\E[Z_i\Delta_i]\Bigr|
\le\sum_i c_i\,\varepsilon_i R_i
=\sum_i \varepsilon_i R_i\,\frac{\hat\sigma_{\mathrm{agg}}^2}{\hat\sigma_i^2},
\]
by the triangle inequality; no independence between the $Z_i$ is needed. The bound controls the \emph{expected} bias---the realised displacement on a contamination event can be as large as $c_iR_i$.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:contradiction}]
Write $C$ for the constraint set of \eqref{eq:rho}, the triples $(\omega',w',M')$ with $q^{(i)}\in\mathcal F((\omega',w',\hat a,\hat f,M',\hat D))$; if $C=\emptyset$ the infimum is $+\infty$ and both directions hold vacuously, so assume $C\neq\emptyset$. The objective is nonnegative, so $\rho^{(i)}\ge 0$ always.

($\Leftarrow$) If $q^{(i)}\in\mathcal F(\hat x)$, the point $(\hat\omega,\hat w,\hat M)\in C$ attains objective zero, so $\rho^{(i)}=0$.

($\Rightarrow$) Suppose $\rho^{(i)}=0$ and take $(\omega'_n,w'_n,M'_n)\in C$ with objective $\to 0$. Because the $M$-penalty is one-sided, this yields $\omega'_n\to\hat\omega$, $w'_n\to\hat w$, and $(M'_n-\hat M)_+\to 0$ only (\emph{not} $M'_n\to\hat M$; $M'_n$ may stay far below $\hat M$), so we pass to the limit through the constraints rather than through the minimiser. Each feasible point has some $\mu_n\in[\mu_{\mathrm{lo}},\mu_{\mathrm{hi}}]$ with $q^{(i)}=1-\omega'_n(w'_n+\mu_n(\hat a-\hat f))/w'_n$. Pass to a subsequence with $\mu_n\to\mu^\ast$ in the compact interval; since $\hat w>0$ and $w'_n\to\hat w$, eventually $w'_n\ge\hat w/2>0$, so the map $(\omega',w',\mu)\mapsto 1-\omega'(w'+\mu(\hat a-\hat f))/w'$ is continuous along the sequence and $q^{(i)}=1-\hat\omega(\hat w+\mu^\ast(\hat a-\hat f))/\hat w$: the exposure constraint holds at the observed $(\hat\omega,\hat w)$. For the manpower constraint, $q^{(i)}\hat D\le M'_n\le\hat M+(M'_n-\hat M)_+\to\hat M$, so $q^{(i)}\hat D\le\hat M$. Both membership conditions of \eqref{eq:feasible} hold at $\hat x$, hence $q^{(i)}\in\mathcal F(\hat x)$.

For the second statement, any rationalisation $(\omega',w',M')\in C$ satisfies, because the infimum lower-bounds the objective on $C$, $\max\{|\omega'-\hat\omega|/\sigma_\omega,\ |w'-\hat w|/\sigma_w,\ (M'-\hat M)_+/\sigma_M\}\ge\rho^{(i)}$; a maximum of three terms is $\ge\rho^{(i)}$ only if at least one term is, so at least one penalised displacement is $\ge\rho^{(i)}$ standardised units. Downward moves of $M'$ are unpenalised by construction and rightly so: they only shrink $\mathcal F$ (the constraint $q\hat D\le M'$ tightens), so they can never rescue a claim.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:robust}]
\emph{(i)} Condition on the realised pattern $T$. The sources outside $T$ are honest, and by the proposition's standing hypothesis every posterior in play is supported on the identified set implied by the sources it uses; a posterior formed from the honest sources plus arbitrary reports from $T$ is therefore supported on the identified set with the $T$-sources removed. Removing sources removes constraints, so this removal set contains the face-value identified set---in particular the face-value posterior support, and with it both $L_0$ and $U_0$---and it has diameter $R_T$ by definition. Any two points of a set of diameter $R_T$ are within $R_T$ of each other, so each endpoint of a support-respecting credible interval (both its endpoints lie in the posterior support, hence in the removal set) is within $R_T$ of the corresponding endpoint of $I_0$.

\emph{(ii)} The contamination indicators are independent, so pattern $T$ realises with probability $P(T)=\prod_{i\in T}\varepsilon_i\prod_{i\notin T}(1-\varepsilon_i)$, and by part (i) the endpoint displacement on that event is at most $R_T$ ($R_\emptyset=0$). Hence the expected displacement is at most $\sum_T P(T)R_T$. Splitting off the singleton patterns and bounding $\prod_{j\ne i}(1-\varepsilon_j)\le 1$,
\[
\sum_T P(T)R_T\;\le\;\sum_i\varepsilon_i R_i+\sum_{|T|\ge 2}P(T)R_T,
\]
and $P(T)\le\varepsilon_{\max}^{|T|}$ makes the second sum $O(\varepsilon^2)$ (it vanishes identically when at most one source can be contaminated). Note that $R_T$ for $|T|\ge 2$ is \emph{not} bounded by $\sum_{i\in T}R_i$ in general (two mutually corroborating sources can each have a small removal diameter while their joint removal is much larger), which is why \eqref{eq:Iepsilon} is stated as a first-order band rather than a uniform envelope.

\emph{(iii)} Write the contaminated posterior as the mixture $\hat F_\varepsilon=(1-\pi)\hat F_0+\pi G$, where $G$ is the (sub-)posterior on contaminated components and $\pi\le\tau$ by assumption. Since $|\hat F_0(x)-G(x)|\le 1$ for all $x$, $\sup_x|\hat F_\varepsilon(x)-\hat F_0(x)|\le\pi\le\tau$. Let $u\in\{\alpha/2,1-\alpha/2\}$ and abbreviate $Q_0=\hat Q_0(u)$, $Q_\varepsilon=\hat Q_\varepsilon(u)$, quantiles taken as generalised inverses. $\hat F_0$ is continuous on the segment in question (it has a density there), so $\hat F_0(Q_0)=u$, and the sup-bound $|\hat F_\varepsilon-\hat F_0|\le\tau$ holds at left limits as well. The generalised inverse satisfies $\hat F_\varepsilon(Q_\varepsilon^-)\le u\le\hat F_\varepsilon(Q_\varepsilon)$, whence
\[
\hat F_0(Q_\varepsilon)-\tau\le\hat F_\varepsilon(Q_\varepsilon^-)\le u
\le\hat F_\varepsilon(Q_\varepsilon)\le\hat F_0(Q_\varepsilon)+\tau,
\]
i.e.\ $|\hat F_0(Q_\varepsilon)-\hat F_0(Q_0)|=|\hat F_0(Q_\varepsilon)-u|\le\tau$,
and since $\hat F_0$ has density $\ge m$ on the segment between $Q_0$ and $Q_\varepsilon$, the left side is $\ge m\,|Q_\varepsilon-Q_0|$; rearranging gives $|Q_\varepsilon-Q_0|\le m^{-1}\tau$. The weight condition is substantive, not automatic: posterior mixture weights are proportional to $P(T)$ times the component marginal likelihoods, so an adversarial component that fits the observed data \emph{better} than the clean model can carry posterior weight exceeding its prior probability $\tau$.
\end{proof}

\section{The spatial Bayesian model}\label{app:spatial}

This appendix documents the forward model, priors, likelihood, and inference behind the posterior reported in Section~\ref{sec:gaza}, Step~5. Code and inputs are in the \texttt{gaza\_sim/} directory of the companion repository, and the posterior is reproducible from a fixed random seed. We emphasise its role: it is \emph{one} model-based point within the assumption-free identified set, and its low posterior $q$ reflects its priors and structural choices as much as the data. Readers who reject those choices should fall back to the bounds, which do not depend on them.

\paragraph{Geometry and population.} Gaza's five governorates are split into $C=400$ equal-population cells (80 per governorate), with cell populations $N_c$ from the PCBS 2023 total. Demographic fractions (women-and-children share $w$, adult-male share $a$) are held constant across cells at the Gaza-wide values.

\paragraph{Latent parameters and priors.} Each posterior draw samples, independently and uniformly on the stated ranges:

\begin{center}
\begin{small}
\begin{tabular}{@{}llll@{}}
\toprule
Parameter & Range & Meaning \\
\midrule
$M$        & $[35\mathrm{k},60\mathrm{k}]$ & total militant stock \\
$\gamma$   & $[0,1.5]$   & spatial clustering amplification of militants \\
$\sigma$   & $[0.3,1.2]$ & SD of the cell-level latent log-density \\
$\alpha$   & $[0,8]$     & strike-targeting concentration on militant density \\
$\beta$    & $[0.6,1.6]$ & targeting non-linearity exponent \\
$\mu_M$    & $[1,2.5]$   & civilian adult-male exposure multiplier \\
$\epsilon_C$ & $[0.7,1]$ & child exposure down-weight \\
$\bar d$   & $[1.2,2.8]$ & expected kills per strike \\
$K$        & $[29\mathrm{k},40\mathrm{k}]$ & total air-to-ground strikes \\
$u$        & $[1/1.7,1]$ & recovery factor (MoH observed $/$ true direct) \\
\bottomrule
\end{tabular}
\end{small}
\end{center}

Militants are allocated across cells proportionally to $N_c\exp(\gamma u_c)$ with $u_c\sim\mathcal N(0,\sigma^2)$, capped at $30\%$ of each cell's adult-male population and rescaled to the total $M$.

\paragraph{Strike-kill model.} Strikes are allocated across cells with weight $N_c(1+\alpha m_c/N_c)^{\beta}$, where $m_c$ is the militant count in cell $c$. Within a cell, a death is a militant, a civilian adult man, or a woman/child with probabilities proportional to $m_c$, $(N_c a - m_c)\mu_M$, and $N_c w\,\epsilon_C$ respectively. Expected class-specific deaths are summed over cells; observed deaths are true direct deaths times the recovery factor $u$.

\paragraph{Likelihood.} Three observables: (i) the MoH cumulative total (log-Gaussian, $7\%$ scale); (ii) the adult-male share among the dead against the OHCHR verified sample (Beta likelihood at its sample size, $n=8{,}119$); and (iii) the same share against the MoH full record, down-weighted to an effective sample size of $n/5$ to reflect cruder demographic categorisation. The two demographic likelihoods enter with weight $1/2$ each.

\paragraph{Inference.} Importance sampling with $2\times 10^5$ prior draws; the effective sample size and all posterior quantiles are computed under the normalised weights. The reported posterior is $q=2.5\%$ (95\% credible interval $[1.6\%,3.8\%]$).

\paragraph{Sensitivities and limitations.} The posterior concentrates at low $q$ for two structural reasons that a critic can legitimately contest: the exposure multiplier prior is capped at $\mu_M\le 2.5$ (values above the cap would push $q$ lower still, but a mass of prior near $\mu_M=1$ pulls the posterior up much less than the OHCHR-weighted demographic likelihood pulls it down), and the OHCHR sample---which over-represents residential-strike deaths where women and children predominate \citep{spagatcockerill2024}---enters the likelihood at full sample weight. Re-anchoring the demographic likelihood entirely on the MoH record moves the posterior median up but keeps it far inside the identified set. Unlike the exposure calibration of Section~\ref{sec:bounds}, the model has not been validated on historical conflicts with known combatant status. Because these choices are contestable, the paper's claims do not rest on this posterior; it appears as one row of Table~\ref{tab:convergence}.

\section{The 81-conflict dataset}\label{app:conflicts}

Table~\ref{tab:all-conflicts} lists every conflict in the dataset behind the overview of Section~\ref{sec:empirical}, with midpoint death totals and the implied civilian-share intervals. The table is generated by the same script that draws Figures~\ref{fig:range-frame} and~\ref{fig:uncertainty-ladder}. The supplementary material provides a single master table detailing the bounds, binding relations, and confidence grades for all 81 conflicts, along with a complete list of primary sources used for each.

\input{\contentroot/tab_all_conflicts.tex}
