%! TEX program = pdflatex
% =====================================================================
% JCR detached title page (uploaded as a separate file in SAGE Track).
% This is the un-blinded title page; the main manuscript (main.tex)
% is the blinded version.
% =====================================================================
\documentclass[12pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}

\begin{document}

\begin{center}
{\LARGE\bfseries Bounds and Estimators for the\\[2pt] Civilian-to-Combatant Death Ratio\\[2pt] from Aggregation of Conflicting Sources}

\vspace{18pt}

{\large David H.\ Silver}\\[6pt]

\textit{Independent researcher}\\
Poughkeepsie, NY 12603, USA

\vspace{4pt}
\href{mailto:silverdavi@gmail.com}{silverdavi@gmail.com}\\
ORCID: \href{https://orcid.org/0000-0002-3071-304X}{0000-0002-3071-304X}

\vspace{20pt}

{\small\textit{Submitted to Journal of Conflict Resolution, Research Article}}

\vspace{6pt}
\today
\end{center}

\vspace{18pt}

\noindent\textbf{Corresponding author.} David H.\ Silver, \href{mailto:silverdavi@gmail.com}{silverdavi@gmail.com}.

\bigskip

\noindent\textbf{Author biographical note.}
David H.\ Silver is an independent researcher based in Poughkeepsie, New York. His peer-reviewed publications appear in \emph{Nature}, \emph{PNAS}, \emph{IEEE Trans.\ Pattern Analysis and Machine Intelligence}, \emph{Human Reproduction}, and \emph{PLOS ONE}; he is the author of the peer-reviewed monograph \emph{Beyond Popular Science} (Open Book Publishers, Cambridge, 2026; DOI \href{https://doi.org/10.11647/OBP.0526}{10.11647/OBP.0526}). He held a Microsoft Research PhD Fellowship in Biomathematics, Bioinformatics, and Computational Biology jointly between the Technion Graduate School and Microsoft Research Cambridge (UK).

\bigskip

\noindent\textbf{Funding.} The author received no specific funding for this work.

\bigskip

\noindent\textbf{Conflicts of interest.} The author declares no conflicts of interest.

\bigskip

\noindent\textbf{Data and code availability.} All data, code, and the Gaza spatial Bayesian simulator will be deposited in a public repository upon acceptance.

\bigskip

\noindent\textbf{Acknowledgements.} The author thanks the editors and anonymous referees for their attention.

\end{document}
