%! TEX program = pdflatex
% =====================================================================
% Annals of Applied Statistics (IMS) submission.
% This file is a journal-ready draft built on the shared master content
% in ../../content/. To swap in the IMS class file:
%
%   1. Download the imsart bundle from
%      https://www.imstat.org/imsart/imsart.zip
%      (provides imsart.cls, imsart-nameyear.bst, imsart-number.bst).
%   2. Replace the preamble below with \documentclass[aoas]{imsart}
%      and follow the imsart user guide; the \input{...} bodies and
%      \bibliography{...} below remain unchanged.
%
% This draft uses an article-class double-spaced layout matching IMS
% submission requirements (one-column, name-year citations).
% =====================================================================
\documentclass[12pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\onehalfspacing
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,multirow,array,tabularx}
\usepackage{graphicx}
\usepackage[hidelinks,colorlinks=false]{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{calc,arrows.meta,decorations.pathreplacing,positioning,fit,backgrounds}
\usepackage[round,authoryear,sort&compress]{natbib}
\bibliographystyle{plainnat}
\captionsetup{font=small,labelfont=bf,labelsep=period,justification=justified}
\setlist{itemsep=2pt,topsep=3pt,parsep=0pt}
\graphicspath{{../../figures/}}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\Ind}{\mathbf{1}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\title{\textbf{Bounds and Estimators for the Civilian-to-Combatant Death Ratio\\ from Aggregation of Conflicting Sources}}
\author{David H.\ Silver\thanks{Independent researcher, Poughkeepsie, NY 12603, USA. Email: \href{mailto:silverdavi@gmail.com}{\texttt{silverdavi@gmail.com}}. ORCID: \href{https://orcid.org/0000-0002-3071-304X}{0000-0002-3071-304X}.}\\
  \small Independent researcher, Poughkeepsie, NY, USA\\[2pt]
  \small\emph{Submitted to Annals of Applied Statistics}}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
\input{../../content/abstract.tex}

\bigskip
\noindent\textbf{MSC2020 subject classifications:} primary 62F15, 62P25; secondary 62G35, 62F35.

\noindent\textbf{Keywords and phrases:} partial identification, robust Bayesian inference, $\varepsilon$-contamination, source aggregation, casualty estimation, Gaza war, contradiction radius.
\end{abstract}

\input{../../content/01_intro.tex}
\input{../../content/02_setup.tex}
\input{../../content/03_bounds.tex}
\input{../../content/04_contradiction.tex}
\input{../../content/05_bias.tex}
\input{../../content/06_gaza.tex}
\input{../../content/07_overview.tex}
\input{../../content/08_discussion.tex}

\paragraph{Acknowledgements.} The author thanks the editors and referees for their attention.

\paragraph{Funding.} The author received no specific funding for this work.

\paragraph{Author affiliation.}
\noindent David H.\ Silver, Independent researcher, Poughkeepsie, NY 12603, USA.\\
\href{mailto:silverdavi@gmail.com}{\texttt{silverdavi@gmail.com}}, ORCID \href{https://orcid.org/0000-0002-3071-304X}{0000-0002-3071-304X}.

\paragraph{Supplementary Material.} A separate document, ``Bounds and Estimators for the Civilian-to-Combatant Death Ratio: Supplementary Material,'' contains the per-conflict tables for the 81-conflict empirical overview, full proofs of Theorem~\ref{thm:bounds} and Proposition~\ref{prop:robust} including measure-theoretic regularity conditions, sensitivity analyses for $\bar\mu$ and $\varepsilon_i$ on the Gaza application, and the reproducibility scripts (\texttt{R}/\texttt{Python} code for the spatial Bayesian sampler).

\bibliography{../../content/refs}

\end{document}
